%-------------------------
% Resume in Latex (developed on Overleaf - https://www.overleaf.com/project/639d4cdaa9ac112e7ca1ce40)
% Author: Sohang Chopra
% Based off of: https://github.com/jakegut/resume
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Sohang Chopra} \\ \vspace{1pt}
    \small Agra, India $|$ \vspace{1pt}
    \small 837-392-6976 $|$ \href{mailto:sohangchopra@gmail.com}{\underline{sohangchopra@gmail.com}} $|$ 
    \href{https://linkedin.com/in/sohang-chopra}{\underline{linkedin.com/in/sohang-chopra}} $|$
    \href{https://github.com/sohang3112}{\underline{github.com/sohang3112}}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Data Analyst/Software Engineer}{January 2022 -- Present}
      {MFilterIt}{Noida}
        \resumeItemListStart
        \resumeItem{Utilized AWS Lambda to systematically extract and analyze data from clients' websites and mobile apps, identifying and addressing faulty content for further analysis.}
        \resumeItem{Collaborated within a cross-functional team of over 10 professionals to architect and implement Flask micro-services tailored for robust data analysis. Focused on ensuring clients' product pages align with CCPA advertising guidelines in India, with a keen emphasis on leveraging data insights for SEO optimization.}
        \resumeItem{Specialized in data processing by training and testing machine learning models using Python, Keras, and PyTorch, with a primary focus on text and image analysis.}
        \resumeItem{Fine-tuned GPT models specifically for natural language tasks, including text detection and generation, enhancing the capabilities of data-driven processes.}
        \resumeItemListEnd
              
    \resumeSubheading
      {Data Analyst (Intern)}{October -- December 2021}
      {Trade Global}{Delhi}
      \resumeItemListStart
        \resumeItem{Analyzed about 10 GB of historical stock data efficiently using Pandas library.}
        \resumeItem{Backtested more than 10 stock exchange strategies via Zerodha Kite API on historical data to select the optimal trading strategies.}
    \resumeItemListEnd

    \resumeSubheading
      {Software Engineer (Intern)}{April –- September 2021}
      {Arcon Cybersecurity}{Mumbai (Remote)}
      \resumeItemListStart
        \resumeItem{Introduced a new flexible GUI Interface for creating automated web tasks using a flow chart using WPF Framework (C\#). These can then be executed easily many times via Selenium (a library for web automation).}
    \resumeItemListEnd

    \resumeSubheading
      {Front End Web Developer (Intern)}{June 2019}
      {Blazar Software Solutions}{Delhi}
      \resumeItemListStart
        \resumeItem{Created beautiful web pages for a project, using Bootstrap components with customized CSS.}
        \resumeItem{Learned about SEO tasks, such as optimizing page load times via Developer Tools.}
    \resumeItemListEnd
        
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart 
        \resumeProjectHeading
            {\textbf{YOLOv5 Image Classification Export} $|$ \emph{Python}}{June 2023}
        \resumeItemListStart
            \resumeItem{Contributed to YOLOv5, an open-source machine learning computer vision framework.}
            \resumeItem{Enhanced \texttt{classify/predict.py} module to export image classification results to CSV for further data analysis.}
        \resumeItemListEnd
    
        \resumeProjectHeading
            {\textbf{Command Line Data Analysis Tool} $|$ \emph{C++}}{March 2018}
        \resumeItemListStart
            \resumeItem{Developed a command line interface for efficient management and analysis of data tables.}
            \resumeItem{Implemented customizable data table creation, modification, and display features, emphasizing robust data handling.}
            \resumeItem{Enabled seamless addition of rows and editing of specific cells or entire rows, ensuring data integrity.}
            \resumeItem{Implemented a powerful search function for locating and analyzing data cells using specified field names.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Dayalbagh Educational Institute}{Agra}
      {Bachelor of Technology in Electrical Engineering, Minor in Computer Science}{July 2018 -- May 2022}
  \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, SQL, HTML / CSS / JavaScript, Bash, C\#, Java, APL (beginner)} \\
     \textbf{Frameworks \& Libraries}{: Numpy \& Pandas, Matplotlib, PyTorch, Tensorflow, Flask, FastApi, Selenium, NodeJS } \\
     \textbf{Skills \& Concepts}{: AWS (Lambda, EC2, S3), Web Scraping, Machine Learning, Docker, Linux, Web Development (Backend + Frontend), Git} \\
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
