%-------------------------
% Resume in Latex (developed on Overleaf - https://www.overleaf.com/project/639d4cdaa9ac112e7ca1ce40)
% Author: Sohang Chopra
% Based off of: https://github.com/jakegut/resume
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Sohang Chopra} \\ \vspace{1pt}
    \small Agra, India $|$ \vspace{1pt}
    \small 837-392-6976 $|$ \href{mailto:sohangchopra@gmail.com}{\underline{sohangchopra@gmail.com}} $|$ 
    \href{https://linkedin.com/in/sohang-chopra}{\underline{linkedin.com/in/sohang-chopra}} $|$
    \href{https://github.com/sohang3112}{\underline{github.com/sohang3112}}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{January 2022 -- Present}
      {MFilterIt}{Noida}
      \resumeItemListStart
        \resumeItem{Scraped clients’ websites \& mobile apps using AWS Lambda to detect faulty content and collect data for analysis.}
        \resumeItem{Member of a product team with over 10 professionals across multiple teams, contributing to the development of Flask micro-services for data analysis to ensure compliance with CCPA advertising guidelines of India.}
        \resumeItem{Developed and tested machine learning models using Keras and PyTorch, fine-tuning GPT models for natural language tasks like text detection and generation.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Data Analyst (Intern)}{October -- December 2021}
      {Trade Global}{Delhi}
      \resumeItemListStart
        \resumeItem{Analyzed 10 GB of historical stock data efficiently with the Pandas library.}
        \resumeItem{Backtested over 10 stock strategies using Zerodha Kite API on historical data to select optimal trading strategies.}
    \resumeItemListEnd

    \resumeSubheading
      {Software Engineer (Intern)}{April –- September 2021}
      {Arcon Cybersecurity}{Mumbai (Remote)}
      \resumeItemListStart
        \resumeItem{Implemented a flexible GUI Interface using WPF Framework (C\#) to create automated web tasks through a flow chart.}
        \resumeItem{Enabled easy execution of created tasks multiple times using Selenium, a web automation library.}
    \resumeItemListEnd

    \resumeSubheading
      {Front End Web Developer (Intern)}{June 2019}
      {Blazar Software Solutions}{Delhi}
      \resumeItemListStart
        \resumeItem{Created beautiful web pages for a project, using Bootstrap components with customized CSS.}
        \resumeItem{Learned SEO tasks, optimizing page load times via Developer Tools.}
    \resumeItemListEnd
        
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart 
      \resumeProjectHeading
          {\textbf{{\underline{IForth (Jupyter kernel for Forth)}}
    \href{https://github.com/sohang3112/iforth}} $|$ \emph{Python, Forth}}{July 2023}
        \resumeItemListStart
            \resumeItem{Forked and revived the abandoned GitHub repository IForth, a Jupyter kernel for the Forth programming language.}
            \resumeItem{Implemented features like code and output prettification, support for running shell commands using the '!' operator, and various bug fixes.}
            \resumeItem{Enhanced stability by implementing kernel termination when the internal GForth process ceases, and included a warning if GForth is not installed.}
            \resumeItem{Added a Dockerfile for easy building and running of IForth within Docker containers.}
            \resumeItem{Published the enhanced version of IForth as a PyPI package to make it easily accessible.}
        \resumeItemListEnd

        \resumeProjectHeading
          {\textbf{{\underline{Login using Face Detection}} 
    \href{https://github.com/sohang3112/face\_login}} $|$ \emph{Python (FastApi), HTML / CSS / JS}}{December 2021}
          \resumeItemListStart
            \resumeItem{Web-based prototype for Login using Face Detection}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{{\underline{Web-based Text Editor}} 
    \href{https://github.com/sohang3112/simple-text-editor}} $|$ \emph{Python (Flask), HTML / CSS / JS}}{October 2021}
          \resumeItemListStart
            \resumeItem{A simple and minimalist web-based text editor, which enables users to create, edit, save, and open text files effortlessly, all developed within 1 day}
          \resumeItemListEnd
              
        \resumeProjectHeading
              {\textbf{Electrical Charge Simulator} $|$ \emph{C++, SFML}}{October 2019}
              \resumeItemListStart
                \resumeItem{Simulated interaction of 100s of randomly charged particles in space.}
                \resumeItem{Studied many interesting phenomena (such as slingshot due to electromagnetic field).}
              \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Dayalbagh Educational Institute}{Agra}
      {Bachelor of Technology in Electrical Engineering, Minor in Computer Science}{July 2018 -- May 2022}
  \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, SQL, HTML / CSS / JavaScript, Bash, C\#, Java} \\
     \textbf{Frameworks \& Libraries}{: Flask, FastApi, Selenium, Node, SFML, WPF Framework for .NET, Numpy \& Pandas, Bootstrap, JQuery} \\
     \textbf{Skills \& Concepts}{: AWS (Lambda, EC2, S3), Docker, Linux, Web Development (Backend + Frontend), Web Scraping, Arduino Programming, MVC, Git} \\
    }}
 \end{itemize}


%----- BEGINNER-PROFICIENCY PROGRAMMING LANGUAGES -----------
\section{Additional Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Haskell (Beginner)}{: Implemented a JSON parser for practice using the Parsec library.} \\
     \textbf{Rust (Beginner)}{: Completed Rustlings (practice exercises for Rust).} \\
     \textbf{Clojure (Beginner)}{: Solved HackerRank problems.} \\
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
