%-------------------------
% Resume in Latex (developed on Overleaf - https://www.overleaf.com/project/639d4cdaa9ac112e7ca1ce40)
% Author: Sohang Chopra
% Based off of: https://github.com/jakegut/resume
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Sohang Chopra} \\ \vspace{1pt}
    \small Agra, India $|$ \vspace{1pt}
    \small 837-392-6976 $|$ \href{mailto:sohangchopra@gmail.com}{\underline{sohangchopra@gmail.com}} $|$ 
    \href{https://linkedin.com/in/sohang-chopra}{\underline{linkedin.com/in/sohang-chopra}} $|$
    \href{https://github.com/sohang3112}{\underline{github.com/sohang3112}}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{January 2022 -- Present}
      {MFilterIt}{Noida}
      \resumeItemListStart
        \resumeItem{Enhanced translation \textbf{efficiency} by over 600\% through \textbf{multithreading} and chunking, streamlining workflow by processing tasks in parallel}
        \resumeItem{Engineered a \textbf{real-time face swap} feature for video streams using \textbf{AWS EC2 GPU server}, enhancing user interaction by integrating celebrity face overlays.}
        \resumeItem{Collaborated in a multi-disciplinary team of 10+ to develop \textbf{Flask microservices} for data analytics with a \textbf{MySQL database}, ensuring CCPA compliance in advertising strategies.}
        \resumeItem{Fine-tuned \textbf{Natural Language Processing} models with \textbf{Keras} and \textbf{PyTorch}, specializing in text detection and generation tasks.}
        \resumeItem{Implemented content monitoring and data collection tools using \textbf{Selenium}, \textbf{AWS Lambda} and \textbf{Pandas} to identify and analyze discrepancies in client web and mobile platforms.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Data Analyst (Intern)}{October -- December 2021}
      {Trade Global}{Delhi}
      \resumeItemListStart
        \resumeItem{Analyzed 10 GB of historical stock data efficiently with \textbf{Pandas} in \textbf{Jupyter Notebook}.}
        \resumeItem{Backtested over 10 stock strategies using Zerodha Kite API on historical data to select optimal trading strategies.}
    \resumeItemListEnd

    \resumeSubheading
      {Software Engineer (Intern)}{April –- September 2021}
      {Arcon Cybersecurity}{Mumbai (Remote)}
      \resumeItemListStart
        \resumeItem{Made a flexible \textbf{GUI} Interface using \textbf{WPF Framework (C\#)} to create automated web tasks through a flow chart.}
        \resumeItem{Enabled easy execution of created tasks multiple times using \textbf{Selenium}, a web automation library.}
    \resumeItemListEnd

    \resumeSubheading
      {Front End Web Developer (Intern)}{June 2019}
      {Blazar Software Solutions}{Delhi}
      \resumeItemListStart
        \resumeItem{Created beautiful web pages for a project, using \textbf{HTML5 \& CSS} with \textbf{Bootstrap} components.}
        % -- MAYBE remove following point - didn't learn much SEO anyway
        \resumeItem{Learned SEO tasks, optimizing page load times via Developer Tools.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects \& Open Source Contributions}
    \resumeSubHeadingListStart 
      \resumeProjectHeading
          %--- Last section empty because date omitted ---%
       {\textbf{\href{https://github.com/python/typeshed/pull/10735}{\underline{Contributor: Flask-SocketIO Type Stubs in Python}}} $|$ \emph{Python, Flask, Open Source}}{}
         \resumeItemListStart
           \resumeItem{Contributed type stub files for Flask-SocketIO (a \textbf{Flask} extension library) in \textbf{Python} typeshed, enhancing static type checking. The pull request was successfully merged.}
        \resumeItemListEnd
    
      \resumeProjectHeading
       %--- Last section empty because date omitted ---%
       {\textbf{\href{https://github.com/sohang3112/iforth}{\underline{IForth (Jupyter kernel for Forth)}}} $|$ \emph{Python, Forth, Open Source}}{}
        \resumeItemListStart
            \resumeItem{Revitalized the abandoned IForth \textbf{Open Source} repository by adding code prettification, shell command support, and stability enhancements including kernel termination management.}
            \resumeItem{Packaged and published the enhanced IForth as a \textbf{Python} package and facilitated deployment with a new \textbf{Dockerfile}, and added documentation for easy use.}
        \resumeItemListEnd

        \resumeProjectHeading
       %--- Last section empty because date omitted ---%
       {\textbf{\href{https://github.com/sohang3112/face\_login}{\underline{Login using Face Detection}}} $|$ \emph{Python (FastApi), HTML / CSS / JS}}{}
        \resumeItemListStart
            \resumeItem{Web-based prototype for Login using \textbf{Face Detection}, with proper usage documentation.}
        \resumeItemListEnd

      \iffalse
      %------ Commented (maybe not that important & impressive?) -----%
      \resumeProjectHeading
        {\textbf{\href{https://github.com/sohang3112/simple-text-editor}{\underline{Web-based Text Editor}}} $|$ \emph{Python (Flask), HTML / CSS / JS}}{October 2021}
          \resumeItemListStart
            \resumeItem{A simple and minimalist web-based text editor, which enables users to create, edit, save, and open text files effortlessly, all developed within 1 day}
          \resumeItemListEnd
        \fi

        \iffalse
        %-- Commented (Kushagara suggested to remove C++ project since not applying for C++) ---%
        \resumeProjectHeading
              {\textbf{Electrical Charge Simulator} $|$ \emph{C++, SFML}}{October 2019}
              \resumeItemListStart
                \resumeItem{Simulated interaction of 100s of randomly charged particles in space.}
                \resumeItem{Studied many interesting phenomena (such as slingshot due to electromagnetic field).}
              \resumeItemListEnd
        \fi
    \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Dayalbagh Educational Institute}{Agra}
      {Bachelor of Technology in Electrical Engineering, Minor in Computer Science}{July 2018 -- May 2022}
  \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, SQL, HTML / CSS / JavaScript, JSON} \\
     %----- Removed (Bash, C++, C#, Java): Kushagara suggested removing ones I'm not that confident in -----%
     \textbf{Frameworks \& Libraries}{: Flask, FastApi, Pydantic, Selenium, Data Exploration with Numpy \& Pandas, Matplotlib} \\
     %----- Removed (WPF Framework for .NET, SFML, Bootstrap, JQuery, NodeJS): Kushagara suggested removing ones I'm not that confident in ----%
     \textbf{Skills \& Concepts}{: AWS (Lambda, Fargate, ECS, EC2, S3), Docker, Linux, MySQL, Jupyter Notebook, Full Stack Web, Web Scraping, Arduino Programming, MVC, Object Oriented Programming, Git, Open Source} \\
    }}
 \end{itemize}

%----- BEGINNER-PROFICIENCY PROGRAMMING LANGUAGES -----------
\section{Additional Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Haskell}: Implemented a JSON \textsf{parser} from scratch using \textsf{Parsec}: \url{https://github.com/sohang3112/json-parser} \\

     \iffalse
     %--- Commented - Kushagara advised to remove langs with no project experience ---%
     \textbf{Rust}{: Completed Rustlings (practice exercises for Rust), Solving Macrokata exercises.} \\
     \textbf{NodeJS/ExpressJS}{: Familiar with creating basic servers using NodeJS and ExpressJS} \\
     \textbf{Clojure}{: Solved HackerRank problems.} \\
     \fi
    }}
 \end{itemize}

%-------------------------------------------------------
\end{document}





